\documentclass{resume}
\begin{document}
\fontfamily{qpl}\selectfont
\noindent
\begin{tabularx}{\linewidth}{@{}m{0.75\textwidth} m{0\textwidth}@{}}
{
    \large\textbf{Jack Van Dyke}\newline
    \small{
         Software Developer - Powell, OH\newline
            \href{mailto:j.vandyket@gmail.com}{j.vandyket@gmail.com}\textbf{ · }
            \href{tel:2342638771}{234-263-8771}\textbf{ · }
            \href{https://github.com/JackTVanDyke}{GitHub Link}\textbf{ · }
            \href{https://www.linkedin.com/in/jack-vandyke}{LinkedIn Link}
    }
}
\newline
\end{tabularx}
\csection{Summary of Qualifications}{\small \noindent \newline Motivated software development student from Columbus State Community College with a 4.0 GPA, 6 months of professional training, industry certifications, and projects utilizing relevant programming languages, frameworks, libraries, and tools. NSF S-STEM IST Scholarship award winner. Looking to use proven programming skills and technical aptitude to meet business needs.
\newline
}
\noindent
\csection{Skills}{\small
    \begin{itemize}
        \item \small{Automation, Testing, Web Development, Machine Learning, Data Analysis, Web Scraping}
        \item \small{HTML, CSS, JavaScript, Java, Python, SQL}
        \item \small{React, NextJS, Spring Boot, Hibernate, AWS, Linux} 
        \item \small{Redux, JUnit, Mockito, TailwindCSS, Pandas, Numpy, Sklearn, BeautifulSoup, Playwright, Jupyter}
        \item \small{Communication, Teamwork, Critical Thinking}
    \end{itemize}
}
\noindent
\csection{Projects}{\small
    \begin{itemize}
        \item \textbf{AYRE}{ - automate your real estate (work in progress for client)}
        {\footnotesize \hspace{8em}\textbf{\href{https://ayre.vercel.app/}{https://ayre.vercel.app/}}}
        \begin{itemize}
            \item \footnotesize {Ayre utilizes NextJS, Prisma ORM, PlanetScale, Clerk, TypeScript, and Vercel to automatically track and provide real estate teams with a dashboard of relevant information from the MLS.}
        \end{itemize}
        
        \item \textbf{NBA Game Prediction ML Model}{ - predicts which NBA team will win with 70 percent accuracy.}
        \begin{itemize}
            \item \footnotesize {I created this in order to learn python, web scraping, process automation, data cleaning, and machine learning. Everything was done inside a Jupyter Notebook.}
            \item \footnotesize {Basketball-reference and rotowire are web scraped for previous box scores and daily lineups.}
            \item \footnotesize {Scraped data is extracted, cleaned, transformed, and loaded into parameter-tuned classifiers to output predictions. Unique advanced player statistics were created in order to increase effectiveness of modeling.}
        \end{itemize}
    \end{itemize}
}
\noindent       
\csection{Experience}{\small
    \begin{itemize}
        \item \textbf{GenSpark - }{Full Stack Java Developer Trainee }\hspace{10em}\textbf{May 2022 – December 2022}
        \begin{itemize}
        \item \footnotesize {Built APIs with Java, Spring Boot, Hibernate, and MySQL utilizing GitHub and Trello within a team environment.}
        \item \footnotesize {Built frontends with React and TypeScript utilizing GitHub and Trello within a team environment.}
        \item \footnotesize {Implemented backend security features with Spring Security, JWT's, Cookies, and Redux.}
        \end{itemize}
    \end{itemize}
}
\noindent    
\csection{Certifications}{\small
    \begin{itemize}
        \item \textbf{Amazon Web Services Cloud Practitioner} \newline
        {\footnotesize {Awarded By: Amazon Web Services}}
        \item \textbf{Java Full Stack} \newline
        {\footnotesize{Awarded By: GenSpark}}
    \end{itemize}
}
\noindent
\csection{Education}{\small
    \begin{itemize}
        % item 1 %
        \item \textbf{Software Developer's AAS - }{Columbus State Community College}\hspace{9.em}\textbf{2023-2024}\newline{GPA: 4.0}
        % item 2 %
        \item \textbf{High School - }{Hudson High School}\hspace{23em}\textbf{2013-2017}\newline{GPA: 4.1}\newline{ACT: 34}
    \end{itemize}
}
\end{document}
